\Large Analyzing the Supreme Court Citation Network

### 2017-12-01 Tex/paper.tex
updating revisions to sections

 \section*{Introduction}

@@

 \section*{The Exponential Random Configuration Model}
Let $c(t)\in \{0,1\}^N$ be a vector indicating which Supreme Court case has been cited at time $t$, where $c_i(t)=1, i \in \{1, \dots , N\}$ indicates that the $i$th case has been cited at time $t$ and $c_i(t)=0$ indicates that the $i$th case has not been cited at time $t$. Furthermore, let
$$\mathcal{C}_t(N)=\{c(t)\in \{0,1\}^N: c_i(t)\in \{0,1\} \}$$ 
be the set of all possible citation combinations at time $t$. Note that the cardinality of $\mathcal{C}_t(N)$ increases exponentially for every newly added case, which results in $2^N$ elements.\\
The probability function of the ERCM is defined as
\begin{equation}
P_{\theta}(c(t)~|~c(t-))=\cfrac{\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}{\sum_{c(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}
\label{ercm}
\end{equation}
where $c(t-)\in \{0,1\}^{N \times (t-1)}$ is a matrix that indicates which cases have been citing in each other before time $t$, $\theta \in \mathbb{R}^q$ is a q-dimensional vector of parameters,  $h: \mathcal{C}_t(N) \to \mathbb{R}^q ~, ~ \c(t) \to (h_1(c(t)), \dots , h_q(c(t)))^T$ is a q-dimensional vector of different statistics and $\kappa(\theta) := \sum_{c(t)^*\in \mathcal{C}}\exp(\theta^T\cdot h(c(t)|c(t-)))$ is a normalization constant that ensures that (\ref{ercm}) defines a probability function on $\mathcal{C}_t$.\\[0.3cm]

@@

\section*{Estimation}

@@

 \section*{Results}
  \subsection*{Descriptive Results}
The supreme court citation network from $1937 - 2005$ consists of $8817$ cases which got voted at $2116$ different time points. The network has a total of $93,263$ ties, of which 452 are mutual. The number of triangles in the network is $211,855$. The in- and outdegree distribution is visualized in figures \ref{indegree_dist} and \ref{outdegree_dist}. The maximum indegree is $190$ and the maximum outdegree is $159$.

@@

\subsection*{Inferential Results}

>>>>

 \section{Introduction}

@@

\section{Network Approaches to Studying Citations}

\textbf{TED}, would you write a section that covers the ways in which network scholars have studied citations in the past, focusing on scientific papers, patents, and court cases?

 \section{The Exponential Random Configuration Model}
Let $c(t)\in \{0,1\}^N$ be a vector indicating which Supreme Court case has been cited at time $t$, where $c_i(t)=1, i \in \{1, \dots , N\}$ indicates that the $i$th case has been cited at time $t$ and $c_i(t)=0$ indicates that the $i$th case has not been cited at time $t$. Furthermore, let
$$\mathcal{C}_t(N)=\{c(t)\in \{0,1\}^N: c_i(t)\in \{0,1\} \}$$ 
be the set of all possible citation combinations at time $t$. Note that the cardinality of $\mathcal{C}_t(N)$ increases exponentially for every newly added case, which results in $2^N$ elements.\\
The probability function of the ERCM is defined as
\begin{equation}
P_{\theta}(c(t)~|~c(t-))=\cfrac{\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}{\sum_{c(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}
\label{ercm}
\end{equation}
where $c(t-)\in \{0,1\}^{N \times (t-1)}$ is a matrix that indicates which cases have been citing in each other before time $t$, $\theta \in \mathbb{R}^q$ is a q-dimensional vector of parameters,  $h: \mathcal{C}_t(N) \to \mathbb{R}^q ~, ~ \c(t) \to (h_1(c(t)), \dots , h_q(c(t)))^T$ is a q-dimensional vector of different statistics and $\kappa(\theta) := \sum_{c(t)^*\in \mathcal{C}}\exp(\theta^T\cdot h(c(t)|c(t-)))$ is a normalization constant that ensures that (\ref{ercm}) defines a probability function on $\mathcal{C}_t$.\\[0.3cm]

@@

\section{Estimation}

@@

 \section{Results}
  \subsection*{Descriptive Results}
The supreme court citation network from $1937 - 2005$ consists of $8817$ cases which got voted at $2116$ different time points. The network has a total of $93,263$ ties, of which 452 are mutual. The number of triangles in the network is $211,855$. The in- and outdegree distribution is visualized in figures \ref{indegree_dist} and \ref{outdegree_dist}. The maximum indegree is $190$ and the maximum outdegree is $159$.

@@

\subsection{Inferential Results}

\textbf{Model updates}
\begin{itemize}
\item Add sender issue area and receiver issue area node covariates (i.e., nodeifactor and nodeofactor applied to issue area). 
\item In the GLM, multiply each variable by the sender time covariate.
\item Write the bootstrap coefficients to a file, send to Bruce so he can write up a code for summarizing the over-time trends in effects.
\item Add a receiver variable (i.e., nodeicov) that equals the absolute difference between the maximum MQ score of a justice in the majority and a minimum MQ score of a justice in the majority.
\item Add a receiver variable (nodeicov) equivalent to the number of justices in the majority

\end{itemize}
